\chapter[Project Proposal]{Project Proposal\\\small{\textit{-- Charles, Justin, Benedict, Jacky}}}
\label{Chapter::Project Proposal}
\index{Chapter!Project Proposal}

% Please describe your project.
% Include a title and a description that includes sample task and DevSecOps tools used, such as source control, testing, deployment, databases, etc.  At this point everything is very vague, but I want you to think about the tools you might need, even if you don't have all the tools very detailed yet.
% 2. Expectations/Rubric for the project:

% The project will be evaluated based on:

% Selected tool, tools or environment
% Building a sample working application (40 pts)
% Using specific tools (DevOps tools) to build a simple project. 
% Ideally, you will try using two comparable tools to do the same project and draw comparisons (security, development, hosting, monitoring, testing, operations, …) (20 pts)
% Use an environment to build the project, AWS, azure or homebrew (containers, micro services, github, …) (20 pts)
% Construct a dashboard reflecting operational aspects (20 pts)
% Construct a modified strength, weakness, opportunities, thread (SWOT) chart for each tool (20 pts)
% Propose something unique


\textbf{Project Title:} Dicey DevOps: A Luck-Based Probability Game
\\

\textbf{Project Description:} Our project is a web-based luck game that also teaches concepts of probability and the idea of risk versus reward. Players will roll dice and place bets on different outcomes such as totals, pairs, triples, or exact numbers. They can choose to re-roll or lock dice, which adds strategic choices between safer but lower-value options and riskier plays with higher potential rewards. The game will also feature occasional "event rounds" where special conditions apply (such as bonus payouts or inverted win conditions). After each round, the game will provide insights into the actual probability of success and expected value, helping players better understand chance, statistics, and decision-making.

Sample tasks include designing the dice roll system with fair randomness, building a leader board to track high scores, and implementing "learning mode" features that explain probabilities to the player. Some tasks we have brainstormed include implementing the dice roll system, building a leader board, and creating a "learning mode" that explains probability insights to players. We will also design a dashboard to track both system health and game-related metrics such as win/loss ratios, re-roll usage, and outcome distributions.

For the DevOps side, we plan to use version control, testing, deployment pipelines, and monitoring tools. Examples may include GitHub for source control, Gitlab CI/CD pipelines to automate builds and deployments, PostgreSQL or another database for storing results, containerization with Docker, infrastructure as code tools for environment setup, and monitoring solutions such as Prometheus and Grafana. We are still discussing the exact tech stack as a team, but our goal is to keep the setup lightweight and easy to extend while still allowing us to compare multiple DevOps tools as required.

